Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-16 article_review/Manuscript.tex
changes manuscript

When $\underline{S}_u$ is small, it usually becomes harder to estimate. For this reason, we consider the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator called ``Correlation 2" has been introduced by Owen in \cite{Owen}. In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices. Our aim is to show that the use of ``Correlation 2" in Variant $A$ may reduce the total number of model evaluations. This new estimator is,
\begin{equation*}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)),
\end{equation*}
where $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. It requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
\bigskip

>>>>

When $\underline{S}_u$ is small, it usually becomes harder to estimate. For this reason, we consider the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator called ``Correlation 2" has been introduced by Owen in \cite{Owen}. In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices. Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple} (Lolo) improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
\begin{equation*}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)),
\end{equation*}
where $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. It requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
\bigskip
